Actuator line modeling of vertical-axis turbines

### 2016-05-12 paper.tex
Remove code listing

turbinesFoam was written in OpenFOAM's style, using OpenFOAM's
\texttt{fvOptions} framework for adding source terms to equations at
runtime---see Listing~\ref{lst:fvOptions} for an example implementation within
the Navier--Stokes' momentum equation. Using the \texttt{fvOptions} framework
allows the CFT-ALM to be added to many of the solvers included in OpenFOAM,
meaning it can be readily used with RANS or LES, multiphase models (e.g., for
simulating the free surface in MHK installations), and even with heat transfer.
This is in contrast to SOWFA's implementation, which requires custom flow
solvers to be developed and maintained.

\begin{lstlisting}[float,language=C++,caption=Adding source terms to the momentum equation in OpenFOAM.,label=lst:fvOptions]
    tmp<fvVectorMatrix> UEqn
    (
        fvm::ddt(U)
        + fvm::div(phi, U)
        + turbulence->divDevReff(U)
        ==
        fvOptions(U)
    );
\end{lstlisting}

>>>>

turbinesFoam was written in OpenFOAM's style, using OpenFOAM's
\texttt{fvOptions} framework for adding source terms to equations at runtime.
This implementation allows the CFT-ALM to be added to many of the standard
solvers included in OpenFOAM without modification, i.e., it can be readily used
with RANS or LES, multiphase models (e.g., for simulating the free surface in
MHK installations), and even with heat transfer.
